\textbf{Computer Science House}\\ Membership Agreement and Code of Conduct

### 2019-08-01 membership-agreement.tex
Clarify that housing registration will not be revoked

\begin{enumerate}
    \item I will abide by the qualifications and expectations of a member,
          as well as follow the general rules of the House, as outlined in the CSH
          Constitution for the entirety of my membership.
    \item I commit to making Computer Science House a friendly and welcoming
          community by embracing the values set forth in this Code of Conduct.
    \item I will abide by the guidelines and rules set forth in the CSH
          Computer Code of Conduct regarding CSH services and member privileges for
          the entirety of my membership.
    \item If I am to fail in the evaluations process, I will revoke my spot
          in the housing queue and on the housing board.
\end{enumerate}

>>>>

\begin{enumerate}
    \item I will abide by the qualifications and expectations of a member,
          as well as follow the general rules of the House, as outlined in the CSH
          Constitution for the entirety of my membership.
    \item I commit to making Computer Science House a friendly and welcoming
          community by embracing the values set forth in this Code of Conduct.
    \item I will abide by the guidelines and rules set forth in the CSH
          Computer Code of Conduct regarding CSH services and member privileges for
          the entirety of my membership.
    \item If I am to fail in the evaluations process, I understand that I will be
          removed from any housing queue or board. If I am already registered to live
          on CSH the following year, I understand my spot will not be revoked.
\end{enumerate}
